---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Lab5PKG

<!-- badges: start -->
  [![R-CMD-check](https://github.com/kanneb/Lab5PKG/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/kanneb/Lab5PKG/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

Lab5PKG is a R package for fetching earthquake data from the USGS Earthquake Catalog API. It will return earthquake data from a specific continent with a specified timeperiod and a minimum magnitude.

## Installation

Install from GitHub. Set the option first if you also want the vignette:

``` r
# install.packages("pak")
options(pkg.build_vignettes = TRUE)
pak::pak("https://github.com/kanneb/Lab5PKG.git")
```

## Example

This is an example of how the package works:

```{r example, warning=FALSE}
library(Lab5PKG)
library(httr2)
library(utils)

df <- earthquake(region = "Africa", starttime = "2020-01-01", endtime = "2021-01-01", min_magnitude = 4)

# Showing the first 10 observations of the earthquake data
head(df, 10)
```

Visualisation of data can be the following

```{r density}
plot(density(df$mag), main = "Distrubution of magnitude", xlab = "Magnitude")
```

# More

The vignette explains every method with examples:

```r 
browseVignettes("Lab5PKG")
```

