---
title: "Earthquake API"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Earthquake API}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Lab5PKG)
```

## Introduction

Lab5PKG fetches earthquake data from the USGS Earthquake API
(<https://earthquake.usgs.gov/fdsnws/event/1/>). The main function,
`earthquake()`, takes a region, a time period and a minimum magnitude,
and returns the matching earthquakes as a data frame.

## Arguments

- `region`: one of `"Europe"`, `"Africa"`, `"Asia"`, `"Oceania"`,
  `"North America"`, `"South America"` or `"Antarctica"`.
- `starttime`, `endtime`: dates as strings in the format `"YYYY-MM-DD"`.
  The end date must be after the start date.
- `min_magnitude`: a single number, 0 or higher.

## Example

Earthquakes in Europe with magnitude 3 or higher during the first ten days of 2026:

```{r}
df <- earthquake("Europe", "2026-01-01", "2026-01-10", 3)
head(df)
```

The returned data frame has the columns `time`, `latitude`, `longitude`,
`depth`, `mag`, `magError`, `place`, `rms` and `type`.

## Invalid input

The function checks its input and stops with an error message if
something is wrong:

```{r, error = TRUE}
earthquake("Linköping", "2026-01-01", "2026-01-10", 3)
earthquake("Europe", "2026-01-10", "2026-01-01", 3)
```

## When no data is returned

- If the search has no matches, an empty data frame is returned.
- If the request fails, for example when there is no internet connection
  or the search exceeds the API limit of 20 000 events, a message is
  printed and the function returns `NULL`.

```{r}
res <- earthquake("North America", "2024-01-01", "2024-12-31", 0)
is.null(res)
empty <- earthquake("Antarctica", "2025-01-01", "2025-01-02", 8)
nrow(empty)
```

